Significant declines in standardised test scores due to COVID-19 school closures disproportionately affect vulnerable students: A replication analysis using data from the United States and a case study on the Netherlands

### 2024-02-15 paper/paper.qmd
Updated Discussion

>>>>

Looking at @fig-race alongside @fig-mathscoresrace and @fig-elascoresrace provides insights into the impacts of virtual schooling. @fig-race demonstrated that districts with higher shares of Black and higher shares of Hispanic students spent more days in virtual schooling as opposed to states with lower shares of these two races. Whilst @fig-mathscoresrace and @fig-elascoresrace show that every race as a whole had lower pass rates in Spring 2021, the difference in pass rates amongst the different races has not significantly changed. This could be evidence that higher rates of virtual schooling did not have a negative impact on test scores, which would indicate that the decline in test scores seen in Spring 2021 was a result of other factors. However, it is important to note that, whilst both @fig-race and @fig-mathscoresrace and @fig-elascoresrace classify districts as being “High” or “Low” based on the shares they comprise of each respective race, Figure \ref{fig-race}’s dataset included data on 48 states, whereas @fig-mathscoresrace and @fig-elascoresrace only had data on 21 states. Moreover, @fig-mathscoresrace and @fig-elascoresrace weighted their results by the total district enrollment. This difference in methodology limits the ability to compare the results represented in the figures.
